---
title: "Linear Models"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)
```

## Load and clean Airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type)


```


Let's fit a model!
```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars + borough, data = _)
fit

# same as:
lm(price ~ stars + borough, data = nyc_airbnb)
```

Look at fit:
```{r}
fit

summary(fit) 
# gives IQR, residuals, all coefficients, SE, t-values, p-values

```

Tidy up output instead:
```{r}
fit |> 
  broom::glance()
```

tidy up coefficients:
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)
# pulls coefficient table as a tibble (dataframe) -- easier to use
```


## Fit another model
```{r}
fit = 
  nyc_airbnb |>
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)) |> # makes manhattan reference and apt ref
  lm(price ~ stars + borough + room_type, data = _)

fit |> 
  broom::tidy()
```



## Look at Diagnostics
```{r}
modelr::add_residuals(nyc_airbnb, fit)
modelr::add_predictions(nyc_airbnb, fit)
```


Like many things in the tidyverse, the first argument is a dataframe. That makes it easy to included steps adding residuals or predictions in pipeline of commands to conduct inspections and perform diagnostics.

```{r}
# violin plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin()

# scatter plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point()

#density plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = resid)) + 
  geom_density() + 
  xlim(-100, 500)
```


## Hypothesis Test for categorical predictor
fit null and alternative model
```{r}
fit_null =  lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt =  lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) |> # compare models
  broom::tidy()
```












