---
title: "Linear Models"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)
```

## Load and clean Airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type)


```


Let's fit a model!
```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars + borough, data = _)
fit

# same as:
lm(price ~ stars + borough, data = nyc_airbnb)
```

Look at fit:
```{r}
fit

summary(fit) 
# gives IQR, residuals, all coefficients, SE, t-values, p-values

```

Tidy up output instead:
```{r}
fit |> 
  broom::glance()
```

tidy up coefficients:
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)
# pulls coefficient table as a tibble (dataframe) -- easier to use
```


## Fit another model
```{r}
fit = 
  nyc_airbnb |>
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)) |> # makes manhattan reference and apt ref
  lm(price ~ stars + borough + room_type, data = _)

fit |> 
  broom::tidy()
```



## Look at Diagnostics
```{r}
modelr::add_residuals(nyc_airbnb, fit)
modelr::add_predictions(nyc_airbnb, fit)
```


Like many things in the tidyverse, the first argument is a dataframe. That makes it easy to included steps adding residuals or predictions in pipeline of commands to conduct inspections and perform diagnostics.

```{r}
# violin plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin()

# scatter plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point()

#density plot
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = resid)) + 
  geom_density() + 
  xlim(-100, 500)
```


## Hypothesis Test for categorical predictor
fit null and alternative model
```{r}
fit_null =  lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt =  lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) |> # compare models
  broom::tidy()
```


## Borough-level differences
```{r}
fit = 
  nyc_airbnb |> 
  lm(price = stars*borough + room_type*borough, data = _) #whether price depends on stars & look at interactions

fit |> 
  broom::tidy()
```


```{r}
airbnb_lm =
  nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    models = map(data, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)) |> 
  select(-data, -models) |> 
  unnest(results)

airbnb_lm |> 
  select(borough, term, estimate) |> 
  mutate(term = fct_inorder(term)) |> 
  pivot_wider(
    names_from = term, values_from = estimate) |> 
  knitr::kable(digits = 2)
```


Same, but a bit different
```{r}
manhattan_airbnb =
  nyc_airbnb |> 
  filter(borough == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb |> 
  nest(data = -neighborhood) |> 
  mutate(
    models = map(data, \(df) lm(price ~ stars + room_type, data = df)), 
    # \(df) gives argument datafram --anonymous function that only exists in this line of code and not in the environment
    results = map(models, broom::tidy)) |> 
  select(-data, -models) |> 
  unnest(results)
```


## Homicides in Baltimore data
```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) |> 
  select(resolved, victim_age, victim_race, victim_sex)
```

Generalized Linear Model
```{r}
fit_logistic = 
  baltimore_df |> 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = _, family = binomial()) # binomial dist.

fit_logistic
```

look at model results
```{r}
fit_logistic |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |>
  select(term, log_OR = estimate, OR, p.value) |> 
  knitr::kable(digits = 3)
```


```{r}
baltimore_df |> 
  modelr::add_predictions(fit_logistic) |> 
  mutate(fitted_prob = boot::inv.logit(pred))
```

